\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{fontawesome5}
\input{glyphtounicode}


%----------FONT OPTIONS----------
% sans-serif
% \usepackage[sfdefault]{FiraSans}
% \usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
% \usepackage[default]{sourcesanspro}

% serif
% \usepackage{CormorantGaramond}
% \usepackage{charter}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.6in}
\addtolength{\evensidemargin}{-0.6in}
\addtolength{\textwidth}{1.2in}
\addtolength{\topmargin}{-.7in}
\addtolength{\textheight}{1.5in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{1pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING----------
\begin{center}
    \textbf{\Huge \scshape Ankit Sahu} \\ \vspace{5pt}
    \small 
    \raisebox{-0.14\height}{\href{tel:+917415773301}{\underline{{\scriptsize \faPhone} +91-7415773301}}} $|$
    \href{mailto:sahu6856@gmail.com}{\underline{{\scriptsize \faEnvelope} sahu6856@gmail.com}} $|$ 
    \href{https://www.linkedin.com/in/ankit-sahu-ind/}{\underline{{\scriptsize \faLinkedin} linkedin.com/in/ankit-sahu-ind}} $|$
    \href{https://ankitsahu.vercel.app/}{\underline{{\scriptsize \faPortrait} portfolio}}
\end{center}


%-----------SUMMARY-----------
\section{Summary}
  Professional with 3+ years of experience in front-end development. Strong background in building web applications and admin panels, as well as in redesigning and refactoring existing codebases.


%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Master of Computer Applications} {Indore, MP}
      {Dr. A.P.J. Abdul Kalam University} {2021 - 2023}
    \resumeSubheading
      {Bachelor of Computer Science} {Gwalior, MP}
      {Govt. Adarsh Science College} {2015 - 2019}
  \resumeSubHeadingListEnd


%-----------PROFESSIONAL EXPERIENCE-----------
\section{Professional Experience}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Web Developer} {Dec 2022 - Present}
      {FitPeo} {Remote}
      \resumeItemListStart
        \resumeItem{Developed and maintained six internal web portals supporting over \textbf{50,000} global admins, patients, providers, and caretakers by writing reusable React components and building end-to-end features.}
        \resumeItem{Published a large feature as a private NPM package to reuse it across all web portals.}
        \resumeItem{Introduced strong typing for existing JavaScript codebase, resulting in 30\% reduction in runtime errors.}
        \resumeItem{Implemented TypeScript and incorporated unit testing framework (Cypress with 90\% coverage), enhancing code quality and application stability.}
      \resumeItemListEnd

    \resumeSubheading
      {Freelance Web Developer $|$ \href{https://www.freelancer.in/u/ankitsahu1}{\underline{profile} {\scriptsize \faExternalLink*} }} {Feb 2021 - Nov 2021}
      {Freelancer.com \& Private Clients}{Remote}
      \resumeItemListStart
        \resumeItem{Developed dynamic websites as per the clients' requirements.}
        \resumeItem{Achieved a \textbf{4.6-star} rating on my Freelance profile from clients.}
    \resumeItemListEnd

    \resumeSubheading
      {Web Developer} {July 2020 - Dec 2020}
      {Binary System} {Gwalior}
      \resumeItemListStart
        \resumeItem{Successfully developed an e-commerce web app using PHP, MySQL, and integrated the Paytm Payment Gateway.}
    \resumeItemListEnd

  \resumeSubHeadingListEnd


%-----------PROJECTS-----------
\section{Projects}
    \small\emph{\textbf{Note: According to the nondisclosure agreement (NDA) in place, live URLs for FitPeo portals cannot shared publicly.}}
    \resumeSubHeadingListStart
      \resumeProjectHeading
          {\textbf{Super Admin, Admin, Patient, Caretaker \& Provider portals}}
          {}
          \resumeItemListStart
            \resumeItem{Technologies used: ReactJS, RemixJS, TypeScript, Redux, Antd, MUI, Tailwind, Cypress.}
            \resumeItem{Completely redesigned and refactored code, completed business requirements, and integrated APIs in all portals.}
            \resumeItem{Improved user experience across all platforms by addressing design flaws \& enhancing overall usability.}
            \resumeItem{Reduced average page load time by 35\% through code optimizations.}
          \resumeItemListEnd
          
      \resumeProjectHeading
          {\textbf{FitPeo Website} $|$ \emph{NextJS, Redux, MaterialUI, Tailwind}}
          {\href{https://www.fitpeo.com/}{\underline{visit site} {\scriptsize \faExternalLink*} }}
          \resumeItemListStart
            \resumeItem{Successfully redesigned and redeveloped the brand website using MUI.}
            \resumeItem{Delivering a visually appealing and modern online presence that effectively showcases FitPeo's offerings.}
          \resumeItemListEnd
          
      \resumeProjectHeading
          {\textbf{TalkGram} $|$ \emph{Socket.io, ReactJS, Redux, MUI, ExpressJS, MongoDB}}
          {\href{https://talkgram.onrender.com/}{\underline{visit site} {\scriptsize \faExternalLink*} }}
          \resumeItemListStart
            \resumeItem{Developed a chat web app to help users connect and share with others, including a group chat feature.}
            \resumeItem{Implemented Google OAuth and sms OTP verification for custom registration.}
            \resumeItem{Integrated with web Socket to make it real time conversation and notifications.}
          \resumeItemListEnd
    \resumeSubHeadingListEnd


%-----------PROGRAMMING SKILLS-----------
\section{Technical Skills}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{Languages/Database}{: JavaScript, TypeScript, HTML/CSS, C/C++, MySql, MongoDB} \\ \vspace{1.5pt}
     \textbf{Libraries/Frameworks}{: React.js, Redux, Remix.js, Next.js, Node.js, Express.js, Material-UI, Antd} \\ \vspace{1.5pt}
     \textbf{Developer Tools}{: Git, GitLab, Jira, Azure DevOps, VS Code} \\ \vspace{1.5pt}
     \textbf{Soft Skills}{: Problem-solving, Team work, Active listening, \textbf{Ownership}}
    }}
 \end{itemize}


%-----------DECLARATION-----------
\section{Declaration}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     In my opinion and knowledge, the information provided above is true and correct.
    }}
 \end{itemize}


%-------------------------------------------
\end{document}
